\newglossaryentry{cosmicshear}
{
    name=Cosmic shear,
    description={Is the distortion of images of high redshift galaxies through the tidal gravitation force of the large scale matter distribution of universe}
}

\newglossaryentry{stamp}
{
    name=Postage stamp,
    description={Small region of a frame, at the same time a frame is small region of all the ccd image. Postage stamp are not used only for the row image. A postage stamp can make reference to the components of a psf model. The import thing is that it refers to a small region of a frame.}
}

\newglossaryentry{mask}
{
    name=Mask,
    description={Grid used to define an specific region of the sky. In general in image analysis masking referees to spatial filtering. }
}

\newglossaryentry{epoch}
{
    name=Epoch,
    description={Exposure. Might be it is ambiguous because each image measure galaxies at different redshift }
}

\newglossaryentry{gclustering}
{
    name=Galaxy clustering,
    description={Technique in observational cosmology that studies the distribution of galaxies from the angular position in the sky}
}

\newglossaryentry{gclusters}
{
    name=Galaxy clusters,
    description={Technique in observational cosmology that studies cosmology from particular clusters of galaxies }
}


\newglossaryentry{gglensing}
{
    name=Galaxy-galaxy lensing,
    description={Technique that studies the shear of background galaxies, around the center of a foreground galaxy. Very useful to understand the relation between the mass and luminosity of galaxies. And confirm the presence of a dark matter halo}
}

\newglossaryentry{S-N}
{
    name=S/N,
    description={Abrevitation of signal to noise }
}

\newglossaryentry{redmapper}
{
    name=REDMAPPER,
    description={It is a galaxy cluster catalog}
}


\newglossaryentry{balrog}
{
    name=BALROG,
    description={Characterizes selection effects and measurement bias by injecting a realistic ensemble of fake star and galaxy images in the real survey data.}
}

\newglossaryentry{COSEBIs}
{
    name=COSEBIS,
    description={Complete Orthogonal Sets of E/B Integrals. Is a general method for computing E/B modes. }
}

\newglossaryentry{Shape noise}
{
    name=Shape noise,
    description={The intrinsic ellipticity of a galaxy is typically one order of magnitude larger than the weak lensing stretching. Shape noise is the standard deviation of the intrinsic ellipticities of galaxies. Therefore, to overcome shape noise we need a large sample of galaxies.  }
}

\newglossaryentry{Noise bias}
{
    name=Noise bias,
    description={When the image is in low S/N regime, pixel noise on the shapes induce a bias. }
}

\newglossaryentry{Model bias}
{
    name=Model bias,
    description={It appears when the galaxies have complex morphology. }
}

\newglossaryentry{SCAMP}
{
    name=SCAMP,
    description={Reads SExtractor catalogs and computes astrometric and photometric solutions for any arbitrary sequence of FITS images. }
}

\newglossaryentry{SWARP}
{
    name=SWARP,
    description={Is a program that resamples and co-adds together FITS images using any arbitrary astrometric projection defined in the WCS standard. }
}

\newglossaryentry{Astrometric solution}
{
    name=Astrometric solution,
    description={Mapping from pixel(x,y) to
sky coordinates( $\theta$ ,  $\phi$) or WCS). This is another source of errors } 
}

\newacronym{CMB}{cmb}{Cosmic Microwave Background}
\newacronym{cdm}{CDM}{Cold Dark Matter}
\newacronym{WCS}{wcs}{World Coordinate System}
\newacronym{nfw}{NFW}{Navarro-Frenk-White}
\newacronym{sed}{SED}{Spectral Energy Distribution}
\newacronym{psf}{PSF}{Point Spread Function}
\newacronym{ir}{IR}{infrared}
\newacronym{nir}{NIR}{near infrared}
\newacronym{hudf}{HUDF}{Hubble Ultra Deep Field}
\newacronym{sdss}{SDSS}{Sloan Digital Sky Survey}
\newacronym{des}{DES}{Dark Energy Survey}
\newacronym{hst}{\textit{HST}}{\textit{Hubble Space Telescope} }
\newacronym{cosmos}{COSMOS}{Cosmic Evolution Survey}
\newacronym{snr}{SNR}{signal-to-noise ratio}


